Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
new latex template

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$
%
%  $Author: ienne, modified by Laurent George $
%  $Date: 2012/02/02 15:20:59 $
%  $Revision: 1.5 $

\documentclass[times, 10pt,twocolumn, a4paper]{article}
\usepackage{latex8}
\usepackage{epsfig, hhline}
\usepackage{amssymb}
\usepackage{vmargin,array,multirow,float,shadow,times, euscript}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{pdftricks}
\usepackage{stmaryrd}

@@

%\newenvironment{accolade}{\begin{centering} $$ \left\{ \begin{array}{l}}{\end{array} \right. $$ \end{centering}}

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
\pagestyle{empty}

%-------------------------------------------------------------------------
\begin{document}

\title{Describing the C-Space of Asynchronous Periodic Task Systems using
Definitive Idle Times}

\author{Thomas Chapeaux, Paul Rodriguez\\
Universit\'e Libre de Bruxelles\\ tchapeau@ulb.ac.be, paurodri@ulb.ac.be \\
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
\and
Laurent George\\
ECE Paris\\
First line of institution2 address\\ Second line of institution2 address\\
lgeorge@ece.fr\\
}

\maketitle
\thispagestyle{empty}

\begin{abstract}
	Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis mi vel
turpis ultricies vulputate vel at arcu. Curabitur lectus metus, rutrum sed malesuada ut, mollis sit amet mauris. Integer dapibus in risus et porttitor. In hac habitasse platea dictumst. Maecenas dolor libero, suscipit porta consequat eu, consequat non orci. Sed tortor neque, tincidunt congue cursus sit amet, luctus id ipsum. Aenean tempor est nisl, at dictum metus elementum iaculis.\\

Keywords: Real-time systems, C-space, WCET, sensitivity analysis
\end{abstract}

@@

	The values of the $n_i$ are given by
	\[
		n_i(t_1, t_2) =
		\left\llbracket
			\left\lfloor
				\frac{t_2 - O_i - D_i}{T_i}
			\right\rfloor -
			\left\lceil
				\frac{t_1 - O_i}{T_i}
			\right\rceil + 1
		\right\rrbracket_0
	\]
	where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.\\

@@

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding at least one synchronous
		instant (an instant at which all tasks release a job simultaneously) out of a
		collection of systems with different offsets. The existence conditions can
		directly be used to calculate the value of the FPDIT (if there is one),
		because for a given set of $a_i$ values they are very similar to an instance
		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}. \\

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
		algorithm into two separate parts. Its global structure is simply a sum of
		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
		be achieved by first computing all possible terms for each task then creating all
		possible DIT values by summing the terms in all possible ways. The number of results is still
		exponential in the number of tasks, but the only operation that is repeated
		exponentially many times is now a sum.

@@

% \nocite{*}
\bibliographystyle{latex8}
\bibliography{dit-paper}

\end{document}

>>>>

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%
\documentclass[conference]{IEEEtran}
\usepackage{cite}
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\fi
\usepackage[cmex10]{amsmath}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{fixltx2e}
\usepackage{url}

% added
\usepackage{amssymb}
\usepackage[ruled,vlined]{algorithm2e}

@@

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Describing the C-Space of Asynchronous Periodic Task Systems using
Definitive Idle Times}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Thomas Chapeaux\\ and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
Adresse\\
Email: tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George\\ and Jean-Fran\c{c}ois Hermant}
\IEEEauthorblockA{ECE Paris\\
Adresse\\
Email}
}
% make the title area
\maketitle

\begin{abstract}
%\boldmath
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis mi vel
turpis ultricies vulputate vel at arcu. Curabitur lectus metus, rutrum sed malesuada ut, mollis sit amet mauris. Integer dapibus in risus et porttitor. In hac habitasse platea dictumst. Maecenas dolor libero, suscipit porta consequat eu, consequat non orci. Sed tortor neque, tincidunt congue cursus sit amet, luctus id ipsum. Aenean tempor est nisl, at dictum metus elementum iaculis
\end{abstract}
% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

  The values of the $n_i$ are given by
  \[
    n_i(t_1, t_2) =
    \left(
      \left\lfloor
        \frac{t_2 - O_i - D_i}{T_i}
      \right\rfloor -
      \left\lceil
        \frac{t_1 - O_i}{T_i}
      \right\rceil + 1
    \right)_0
  \]
  where $( x )_0$ stands for $\max \{ 0, x \}$.\\

@@

  \subsection{Solving the modular system}
    Finding the FPDIT of a system is similar to finding a synchronous instant of
    this system (an instant at which all tasks release a job simultaneously), but
    with weaker constraints. That is, the FPDIT is an instant after the last
    deadline of all tasks, but before the next arrival time of all tasks. Finding
    a synchronous instant is equivalent to finding a solution $t$ for the
    following set of constraints :
    \[
      \left\{
      \begin{array}{l}
        t \geqslant O_i \: \forall \: \tau_i \in \tau \\
        t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
      \end{array}
      \right.
    \]
    which is very similar to an instance of the Chinese Remainder Problem (CRP). It
    is not possible to directly use a solver for the CRP (such as Gauss's
    algorithm \cite{gauss1965disquisitiones}) as in a task system, $T_i$ values could have common factors.
    However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
    without changing the solution if there is one) in order to make the problem
    solvable through applying a solution for the CRP. \\

    Now that we have a solver for the problem of finding a synchronous instant, we
    actually also have a solver for finding the FPDIT. The problem of finding the
    first DIT is the same as finding all the possible DIT then taking the minimum.
    Each of those DIT corresponds to a unique combination of $a_i$ values (one
    for each task). Finding one of such DIT is the same problem as finding a
    synchronous instant :
    \[
      \left\{
      \begin{array}{l}
        t \geqslant O_i + a_i \: \forall \: \tau_i \in \tau \\
        t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
      \end{array}
      \right.
    \]
    all DITs can be found by solving the equivalent CRP problem for all
    combinations of $a_i$ values. This is however very inefficient as there are
    exponentially many different combinations of $a_i$ values in the number of
    tasks.\\

    A better method for finding the FPDIT consists in splitting Gauss's algorithm
    into two separate parts. The global structure is simply a sum of factors, each
    term being dependent on which $a_i$ value is chosen. A major speedup can
    be achieved by first computing all possible terms for each task (only one
    modular inverse must be computed per task that way) then creating all possible DIT values
    by summing the terms in all possible ways. The number of results is still
    exponential in the number of tasks, but the only operation that is repeated
    exponentially many times is now a sum.

@@

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}
